### 2015-11-13 postdoctoral/gamma_functions.tex
make metrizability result explicit

  \begin{theorem}
    \(\check L\) is metrizable if and only if \(L\) is countable.
  \end{theorem}

  \begin{proof}
    If \(L\) is uncountable, let \(\mc B\) be a base for \(\check L\).
    For each \(l\in L\), there is some neighborhood \(B_l\in\mc B\) of
    \((\leftarrow,l)\) which is a subset of
    \([\emptyset,(\leftarrow,l])=[\emptyset,(\leftarrow,l)]\). Each \(B_l\)
    is unique, so \(\check L\) is compact but not second countable,
    and therefore nonmetrizable.

    If \(L\) is countable, then note that the union of
    \(\mc S=\{((\leftarrow,l),L]:l\in L\}\) and
    \(\mc T=\{[\emptyset,(\leftarrow,l]):l\in L\}\)
    generates a countable base for \(\check L\). Thus \(\check L\) is
    compact second-countable, and therefore metrizable.
  \end{proof}

@@

>>>>

  \begin{theorem}
    \(\check L\) is second-countable if and only if \(L\) is countable.
  \end{theorem}

  \begin{proof}
    If \(L\) is uncountable, let \(\mc B\) be a base for \(\check L\).
    For each \(l\in L\), there is some neighborhood \(B_l\in\mc B\) of
    \((\leftarrow,l)\) which is a subset of
    \([\emptyset,(\leftarrow,l])=[\emptyset,(\leftarrow,l)]\). Each \(B_l\)
    is unique, so \(\check L\) is not second-countable.

    If \(L\) is countable, then note that the union of
    \(\mc S=\{((\leftarrow,l),L]:l\in L\}\) and
    \(\mc T=\{[\emptyset,(\leftarrow,l]):l\in L\}\)
    generates a countable base for \(\check L\).
  \end{proof}

  \begin{corollary}
    \(\check L\) is metrizable if and only if \(L\) is countable.
  \end{corollary}

@@

  \begin{corollary}
    If \(f\) is a non-trivial V-map satisfying condition \(\Gamma\), then
    \(\varprojlim \{X, f, L\}\) is metrizable if and only if
    \(X\) is metrizable and \(L\) is countable.
  \end{corollary}

  \begin{proof}
    If \(X\) is metrizable and \(L\) is countable, then of course
    \(\varprojlim \{X,f,L\}\subseteq X^L\) is metrizable. If \(X\) is
    nonmetrizable, then \(\varprojlim \{X,f,L\}\) cannot be metrizable
    as it contains a copy of \(X\). Finally, if \(L\) is uncountable,
    then \(\varprojlim \{X,f,L\}\) cannot be metrizable as it
    contains a copy of \(\varprojlim \{2,\gamma,L\}\cong\check L\).
  \end{proof}
